\documentclass[letterpaper]{article}
\usepackage{plainresume}
\usepackage{multicol}

\pagestyle{plain}

\begin{document}
\title{William Fisher}
\author{}

\begin{multicols}{3}
\begin{list1}
  \item \begin{tabular1bold} williamsykesfisher@gmail.com \end{tabular1bold}
  \item \begin{tabular1bold} +44 7904 428 806  \end{tabular1bold}
  \item \begin{tabular1bold} http://github.com/filwisher \end{tabular1bold}
\end{list1}
\end{multicols}

\section*{Summary}
\begin{list1}
  \item \emph{C}, \emph{Haskell}, \emph{Javascript}, \emph{Go}.
  \item Background in programming, distributed systems, and type theory. Experience with Linux, web servers, and databases. Interested in functional programming, systems programming, mathematics, and cooperatives. 
\end{list1}


\section*{Education}
\begin{list1}
  \item \begin{tabular1bold} MSc. Computing Science, Imperial College & 2015 -- Present \end{tabular1bold}
  \vspace{-2ex}
  \begin{list2}
    Modules in Networks and Distributed Systems, Concurrency, Algorithms, and Robotics. Group project in content-based network protocols. Individual project in type theory and Haskell.
  \end{list2}
  
  \item \begin{tabular1bold} Collective Academy, Camden Collective & 2014 \end{tabular1bold}
  \vspace{-2ex}
  \begin{list2}
    Peer-led course in web development. Curriculum covered: version control (Git), automated testing, agile practices, data visualization (D3.js), and web-server programming (Node.js).
  \end{list2}
  
  \item \begin{tabular1bold} BA Music, University of Leeds (First Class) & 2011 -- 2014 \end{tabular1bold}
  \vspace{-2ex}
  \begin{list2} 
  Modules in Composition (indeterminate, algorithmic, cellular-automata), Aesthetics and Criticism (phenomenological, post-structuralist, feminist), Music Technology (\emph{Supercollider}, \emph{MaxMSP}). Dissertation on aesthetics of sexualization in popular music.
  \end{list2}
  
  \item \begin{tabular1bold} Fortismere Secondary School & 2006 -- 2010 \end{tabular1bold}
  
  \begin{list2} 
    \item \textbf{A Levels}: Philosophy \emph{A}, Mathematics \emph{B}, Music \emph{C}
    \item \textbf{GCSEs}: 2 \emph{A*}, 5 \emph{A}, 3 \emph{B}
  \end{list2} 
  
\end{list1}

\section*{Employment}
 
\begin{list1}
  \item \begin{tabular1bold} Software Developer and Teacher, Founders \& Coders & 2014 -- 2015 \end{tabular1bold}
  
  \begin{list2} 
    Founding member of an award-winning web development cooperative. Responsibilities included planning project architecture and implementation details, and teaching groups of 16 students how to write web-based applications.
  \end{list2} 
  
\end{list1}

\section*{Projects}
\begin{list1}
  \item \begin{tabular1bold} Camden Maps, Camden Council -- \emph{http://maps.camden.gov.uk} & 2014 -- 2015 \end{tabular1bold}
  
  \begin{list2} 
    Lead developer in a 4-person team contracted by Camden Council to build a service for finding local amenities and live information about street works. Updated an undocumented, legacy API from SOAP to RESTful. 
  \end{list2} 
  
  \item \begin{tabular1bold} Founders \& Coders -- \emph{http://www.foundersandcoders.org} & 2014 -- 2015 \end{tabular1bold}
  
  \begin{list2} 
    Helped start a cooperative with the aims of providing free, full-time coding courses and helping course graduates to find employment as web developers. 
  \end{list2} 
  
\end{list1}

\section*{Prizes}
\begin{list1}
  \item \textbf{Young Cooperator's Prize, AltGen}: Awarded to Founders \& Coders for our innovation and commitment to cooperative values.
  \item \textbf{Lord Snowdon Prize, University of Leeds}: Awarded for notable achievement in Music, for graduating with the highest grade in the year.
\end{list1}

\section*{Miscellaneous}
  
\begin{list1}
  \item \textbf{Interests}: Functional programming, type theory and category theory, language design, systems programming: compilers and operating systems, networking: distributed systems and peer-to-peer, almost everything.
  \item \textbf{Skills}: Web development, SQL and NoSQL databases, browser and web server programming, teaching, algorithms, concurrency, and networks.
  \item \textbf{Languages}: \emph{Javascript} and \emph{Nodejs} (fluent); \emph{C}, \emph{C++}, \emph{Java}, \emph{Prolog} (familiar); \emph{Go} and \emph{Haskell} (currently pursuing). Very interested in learning new languages.
\end{list1}

\end{document}
